---
title: "Analysis of 2015 Movies Data"
output: html_notebook
---

# Prepare Data
```{r, results='hide'}
library(tidyverse)
library(magrittr)
library(lubridate)

## eg: 2015072700 - remove last 2 positions, and convert to date
to_ymd <- . %>% as.character %>% substr(., 1, nchar(.)-2) %>% ymd
standardize_title <- . %>% tolower %>% gsub(" \\([^()]+\\)", "", .)
```

```{r, results='hide', message=FALSE}
boxoffice <- read_csv("../cache/boxoffice.csv") %>% select(-X1)
views <- read_csv("../cache/views.csv") %>% select(-X1)
edits_users <- read_csv("../cache/edits_users.csv") %>% select(-X1)
```

```{r, results='hide'}
views$timestamp %<>% to_ymd
boxoffice$title %<>% standardize_title
views$title %<>% standardize_title
edits_users$title %<>% standardize_title
```

```{r, results='hide'}
views30 <- views %>%
    group_by(article) %>%
    arrange(timestamp) %>%
    slice(1) %>%
    ungroup

df1 <- left_join(
    views30,
    edits_users %>% select(-end_dt),
    by="title") 
```

```{r, results='hide'}
## check some rows
## df1 %>% select(title, timestamp, begin_dt) %>% sample_n(10)
## eg, tangerine
## views %>% filter(article=="Tangerine")
```

# Obtain analysis data frame
```{r, results='hide'}
df1 %<>% select(title, views, revisions, users) %>% na.omit

df <- df1 %>%
    left_join(
        .,
        boxoffice %>% select(title, domestic, genre, mpaa_rating, production_budget, runtime),
        by="title")
```
# Model: Caveats
The model results follow. In summary, it seems we CAN make quite good predictions, but there are a few caveats:

* the below predicts DOMESTIC boxoffice revenue based on activity 30 DAYS BEFORE the movie release (usually 30 days. had a few errors where data is from closer, like 10 days before release. to discuss)
* this is preliminary, since there is a bunch of missing movies (rough guess is 40%), but we still have good results. with some work, we can up this % since the missing data is fixable (to discuss)
* but there is good news: I was able to easily obtain additional data on things like movie genre and runtime, which provide very good predictions, based on first look! see the second model



# Model 1
See the R-squared statistic (ranges from 0 to 1, higher is better)

```{r}
mod <- lm(domestic ~ views + revisions + users, data=df)
mod %>% summary
```

# Model 2
```{r}
mod <- lm(domestic ~ views + revisions + users + runtime +
            factor(genre) + factor(mpaa_rating) + production_budget,
          data=df)
mod %>% summary
```
